Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2015-08-30 patchy-review-responses-second-round.tex

\vskip 2em

\noindent
{\bf To the Editor(s) -- }

\vskip 1em

\begin{quote}
    Both reviewer 1 and reviewer 2 still question your main result presented in Eq. 11 and I do agree with them that there is definitely something wrong with the dimensions. 
    % This was already pointed in the first round of reviews and both reviewers feel that this issue has not been satisfactorily addressed. 
\end{quote}

\begin{quote}
    Both reviewer also argued in the first round that the derivations in the paper are overly complicated and that the problem can in fact be intuitively understood via much simpler arguments (both came up with very similar approaches independently). 
    You stated in your replies that you prefer to stick with your derivation because you consider it more solid. 
    However, I am not even fully convinced that your Eq. 11 is more correct than the reviewers' intuitive results. 
\end{quote}

\begin{quote}
    Reviewer 1 points out that there are quite substantial deviations in your numerical results (Fig. 4) and reviewer 2 stresses that the 1D simulations won't even be able to catch the potential problems associated with the boundary of the target area. Clearly, something is not yet fully understood here and I don't see how the paper can be accepted without having settled these issues.
\end{quote}

% \begin{quote}
    % It would be easy to simply reject the paper at this point.  However, as I expressed earlier, I still think that this is an extremely interesting problem that could be of great relevance for future studies, given that the authors can convincingly resolve the issues raised above. The dimensionality problem clearly needs to be resolved, and it needs to be explained how their result and the intuitive results from the reviewers compare with each other.
% \end{quote}

\begin{quote}
    I also think that presenting and discussing the intuitive results really would be important for the paper, as originally suggested by reviewers 1 and 2. There is a tendency in population genetics to derive complicated ``exact'' results that are nonetheless of only limited usefulness in reality because it's unclear how realistic the underlying models are in the first place. I won't hide here that I strongly prefer a heuristic approach that reveals what's actually going on, over a lengthy technical calculation that may be formally more correct, yet it's unclear whether this really matters in reality. I feel the majority of the audience of PLoS Genetics is probably with me on this.
\end{quote}

% \begin{quote}
%     Should you decide to tackle these problems in a major revision, please also address the remaining comments raised by the reviewers. Sorry that I can't bring you better news at this point but I think you will agree that the reviews are pretty clear in what needs to be done in order to get this paper accepted in PLoS Genetics.
% \end{quote}

@@

{\bf Peter Ralph, and\\
Graham Coop.}\\
\end{minipage}

\vskip 4em

\reply

The main change,
which addresses most of the concerns,
is that we uncovered an error in the derivation of equation \eqref{eqn:migrate},
that supplied the missing factor of area noted by the reviewers.
The error occurred in the transition between section \nameref{ss:heuristics} 
and section \nameref{ss:hitting_occupation}
because in the former we had tried to keep things simple
by not including shape of the patch in
gestalt equations \eqref{eqn:gestalt_q} and \eqref{eqn:gestalt_migrate},
but then (more correctly) treated the shape in the latter;
effectively we were treating the patch as very small in one place
and large in another.
We've rewritten the argument in \nameref{ss:heuristics} 
to deal explicitly with the integral over the whole patch,
which also necessitated adding a new (short) section \nameref{apx:qS}.
Section \nameref{ss:hitting_occupation} required very little change.

@@

%%%%%
\point{line 262:}{
    cut "depends" (?)
}

\reply
Also done, thanks.

%%%%%
\point{line 263:}{
    time to reach 100 B alleles: simulations should show how long this takes $\to$ can this explain anything or is it irrelevant? (Unclear in Fig 4 since value for $s_p$ is not provided).
}

\reply
In all the simulations, we fixed $s_p=0.01$ (now stated),
which measured in terms of instantaneous growth is a selection coefficient of about 0.002.
It's not at all straightforward to determine when the originating mutation arose,
since this would require tracing lineages back -- doable, but a lot more work.
Also, it seems that the second issue -- not really treating the boundary correctly
-- is more significant than the time the numbers take to go from 1 to 100.
Taking these two together,
and not wanting to further complicate the paper,
we decided to not try to pursue this farther.

### 2015-08-30 patchy-selection-paper.tex
.

\begin{figure}[ht!]
  \begin{center}
      % made in analyze-sims.R
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(left)} 
      Time until adaptation by mutation in an isolated patch for different combinations
      of selection coefficient on patches ($s_m$), 
      population density ($\rho$),
      mutation rate ($\mu$),
      and distance between patches ($R$), \revpoint{3}{3}
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:mutrate} (horizontal axis).
      In all simulations, $s_p=0.01$.
      \textbf{(right)} 
      Time until adaptation by migration from an already occupied patch to a new patch,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:migrate}, with $C=5$ (horizontal axis).
      For each,
      parameter combinations and numbers of simulations are in supplemental tables \ref{stab:mutation_params} and \ref{stab:migration_params};
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination.
      Only parameter combinations to which the theory here is applicable were used
      (precisely, if
      $R > \sigma/\sqrt{s_m}$, 
      patch width larger than $\sigma/\sqrt{s_m} \atan(\sqrt{s_m/s_p})$, 
      and $s_m > 2 \sigma \rho$);
      the remaining combinations are shown in figures
      S\ref{sfig:sim_migration_times} and S\ref{sfig:sim_mutation_times}.
  }   \label{fig:sim_times}
\end{figure}

>>>>

\begin{figure}[ht!]
  \begin{center}
      % made in analyze-sims.R
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(left)} 
      Time until adaptation by mutation in an isolated patch for different combinations
      of selection coefficient on patches ($s_m$), 
      population density ($\rho$),
      mutation rate ($\mu$),
      and distance between patches ($R$), 
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:mutrate} (horizontal axis).
      In all simulations, $s_p=0.01$.
      \textbf{(right)} 
      Time until adaptation by migration from an already occupied patch to a new patch,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:migrate}, with $C=5$ (horizontal axis).
      For each,
      parameter combinations and numbers of simulations are in supplemental tables \ref{stab:mutation_params} and \ref{stab:migration_params};
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination.
      Only parameter combinations to which the theory here is applicable were used
      (precisely, if
      $R > \sigma/\sqrt{s_m}$, 
      patch width larger than $\sigma/\sqrt{s_m} \atan(\sqrt{s_m/s_p})$, 
      and $s_m > 2 \sigma \rho$);
      the remaining combinations are shown in figures
      S\ref{sfig:sim_migration_times} and S\ref{sfig:sim_mutation_times}.
  }   \label{fig:sim_times}
\end{figure}
